Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-08-21 manuscripts/manuscript.Rmd
update theme and libraries, rebuild cache

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")

options(digits=2)

theme_set(theme_tufte() + theme(axis.line = element_line())
```

>>>>

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
library("dplyr")
library("tidyr")
options(digits=2)

theme_set(theme_tufte() + theme(axis.line = element_line()))
```
